Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 approach.tex
red thing

Whitening the non-zero
feature vector $x'$ means a solving the system of linear equations, $\Sigma' w' = (x' -
\mu')$. In
\cite{Hariharan12}, the authors make use of the fact that covariance matrices
are symmetric and positive semidefinite to solve the system via the Cholesky
decomposition with Gaussian Elemination, which requires $O(n^3)$ time \scream{Citation for complexity}.

The Conjugate Gradient method is an iterative algorithm for solving symmetric
positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
the condition number of the matrix. \scream{Citation for complexity}.
%
This makes Conjugate Gradient faster than decomposition for matrices with small condition
numbers relative to their size.

>>>>

Whitening the non-zero
feature vector $x'$ means a solving the system of linear equations, $\Sigma' w' = (x' -
\mu')$. In
\cite{Hariharan12}, the authors make use of the fact that covariance matrices
are symmetric and positive semidefinite to solve the system via the Cholesky
decomposition with Gaussian Elemination, which requires $O(n^3)$ time.

The Conjugate Gradient method is an iterative algorithm for solving symmetric
positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
the condition number of the matrix. \cite{Shewchuk94}.
%
This makes Conjugate Gradient faster than decomposition for matrices with small condition
numbers relative to their size.

### 2014-11-14 experiments.tex
red thing

To that end, we create an ensemble of NZ-WHO templates (Sect.~\ref{})
using $9$ different CAD models and a total of \scream{} different
viewpoints, using $X$ different evelation angles, $X$ azimuth angles,
and $X$ focal lengths. We run the entire ensemble exhaustively over
each test image, in a sliding window fashion.

@@

For both cases, we compare the performance of a discrete incarnation
of our method (Sect.~\ref{}) and our full model, including the
fine-tuning based on MCMC~\cite{Sect.~\ref{}}

@@

 More qualitative results are part of
supplemental material~\scream{}

@@

\begin{tabular}{|c|c|c|c|c|}

>>>>

To that end, we create an ensemble of NZ-WHO templates (Sect.~\ref{sec:approach})
using $9$ different CAD models and a total of 192 different
viewpoints, using 4 different evelation angles, 24 azimuth angles,
and 2 focal lengths. We run the entire ensemble exhaustively over
each test image, in a sliding window fashion.

@@

For both cases, we compare the performance of a discrete incarnation
of our method (Sect.~\ref{sec:approach}) and our full model, including the
fine-tuning based on MCMC~\cite{Sect.~\ref{sec:tuning}}

@@

 More qualitative results are part of
supplemental material

@@

\begin{tabular}{|ccccc|}
